Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-10 paper_jasa.tex
colours added on p-value-log-count plot based on the observed data plot p-value
typo in proof
exclusion criteria

This proves the statement above. We further see:
\[
E\left[ (1 - p_D)^{m-1}\right] =  \sum_{k=0}^{m-1} {m-1 \choose k} (-E[p_D])^{k} = 1-(m-1)E[p_D] + O(E[p_D^2]).
\]
This implies that as $p_D$, the $p$-value, becomes smaller, the probability that the observer identifies the data plot goes up and,
conversely, as $m$, the number of choices given in the lineup, goes up the probability to pick the data plot  goes down. 
}
%
%
%
%Let us think of a lineup as a head-to-head comparison of the test statistic and $m-1$ null plots. 
%%Let the data plot have a $p$-value of $p_D$, and the null plots $p$ values of $p_{0, i}$ with $1 \le i \le m-1$.
%We know that for each comparison the probability that the data, on which the plot is based, has the smaller $p$ value is 
%\begin{eqnarray*}
%P(p_D < p_{0,i}) &=& 1 - P(p_{i,0} \le p_D) = 1- \int_0^1  P(p_{i,0} \le p_D \mid p_D=t) f_{p_D}(t) dt =  \\
%&=& 1 - \int_0^1 F_{p_{0,i}}(t) f_{p_D}(t) dt = 1 - \int_0^1 t f_{p_D}(t) dt = 1 - E[p_D],
%\end{eqnarray*}
%which, in particular, is independent of $p_{0,i}$ for all $i$.
%
%Let us make the assumption that an observer is able to identify  the chart corresponding to the data with the smallest $p$-value. Further we will assume that all observers  have the same ability in identifying the data plot.
%
%With that, we define $Z$  as the number of null plots in a lineup, for which the $p$-value $p_{0,i}$ is smaller than $p_D$.  
%
%Then $Z \sim B_{m-1, E[p_D]}$, and the probability that an observer will pick the data plot in a given lineup is 
%\[
%P(Z=0) = \left(1 - E[p_D] \right)^{m-1} = P(p_D \le p_0), \ \ \ \text{ where } p_0 = \min_{1 \le i \le m-1}  \ p_{0,i}.
%\]
\end{proof}

@@

\subsection{Data Cleaning}

% In this process of collecting data some participants did not provide demographic information as we see in Table \ref{tbl:summary} that male and female participants do not add up to total participants. It is not clear why they did not provide the information. Now the concern arises whether we should keep their responses in the study. It is also possible that participants were not serious enough to provide feedback. 
For each of the experiments we had a test plot (easy plot) for which they should have a correct evaluation without much effort.  This could be a criteria to determine their attentiveness in the study. For this we consider six different data cleaning criteria as shown below;

{\bf Cleaning data:} There are six suggested approach to clean the data. They are 
\begin{enumerate}
\item not throw out anything
\item throw out people where we don't have demographic information
\item throw out all people with 0 percent correct
\item only include people with at least 20 percent correct (current suggestion)
\item include people with 50\% correct on all very easy (could be evaluated correctly if the participant is not ignorant) lineups (as suggested before)
\item each person saw at least one easy lineup. we select one of those easy lineups as the inclusion criteria. If that lineup is evaluated correctly we include only the rest of the evaluations of that subject. Otherwise, we exclude all the feedbacks of that subject.
\end{enumerate}

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets.}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 &  98 &  64 &  34 & 1095 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_log_counts.pdf}}
       \caption{Frequency of plot picks by log$_10$ $p$-value in individual lineups}
       \label{fig:P-val_log}
\end{figure*}

>>>>

This proves the statement above. We further see:
\[
E\left[ (1 - p_D)^{m-1}\right] =  \sum_{k=0}^{m-1} {m-1 \choose k} (-1)^k E[p_D^k] = 1-(m-1)E[p_D] + O(E[p_D^2]).
\]
This implies that as $p_D$, the $p$-value, becomes smaller, the probability that the observer identifies the data plot goes up and,
conversely, as $m$, the number of choices given in the lineup, goes up the probability to pick the data plot  goes down. 
}
%
%
%
%Let us think of a lineup as a head-to-head comparison of the test statistic and $m-1$ null plots. 
%%Let the data plot have a $p$-value of $p_D$, and the null plots $p$ values of $p_{0, i}$ with $1 \le i \le m-1$.
%We know that for each comparison the probability that the data, on which the plot is based, has the smaller $p$ value is 
%\begin{eqnarray*}
%P(p_D < p_{0,i}) &=& 1 - P(p_{i,0} \le p_D) = 1- \int_0^1  P(p_{i,0} \le p_D \mid p_D=t) f_{p_D}(t) dt =  \\
%&=& 1 - \int_0^1 F_{p_{0,i}}(t) f_{p_D}(t) dt = 1 - \int_0^1 t f_{p_D}(t) dt = 1 - E[p_D],
%\end{eqnarray*}
%which, in particular, is independent of $p_{0,i}$ for all $i$.
%
%Let us make the assumption that an observer is able to identify  the chart corresponding to the data with the smallest $p$-value. Further we will assume that all observers  have the same ability in identifying the data plot.
%
%With that, we define $Z$  as the number of null plots in a lineup, for which the $p$-value $p_{0,i}$ is smaller than $p_D$.  
%
%Then $Z \sim B_{m-1, E[p_D]}$, and the probability that an observer will pick the data plot in a given lineup is 
%\[
%P(Z=0) = \left(1 - E[p_D] \right)^{m-1} = P(p_D \le p_0), \ \ \ \text{ where } p_0 = \min_{1 \le i \le m-1}  \ p_{0,i}.
%\]
\end{proof}

@@

\subsection{Data Screening}

% In this process of collecting data some participants did not provide demographic information as we see in Table \ref{tbl:summary} that male and female participants do not add up to total participants. It is not clear why they did not provide the information. Now the concern arises whether we should keep their responses in the study. It is also possible that participants were not serious enough to provide feedback. 
%For each of the experiments we had a test plot (easy plot) for which they should have a correct evaluation without much effort.  This could be a criteria to determine their attentiveness in the study. For this we consider six different data cleaning criteria as shown below;

{\bf Screening scenarios:} \hh{Amazon Mechanical Turk data often suffers from the problem that some participants are trying to 'game' the system -- in our situation, these are participants who did not put in a best effort to identify the data plot, but just randomly picked a plot to maximize their 'winnings'.  In order to avoid using those results, we are comparing six different screening methods for excluded participants from the data analysis.} 
%There are six suggested approach to clean the data. 
They are 
\begin{enumerate}
\item {\bf include all participants} and their evaluations
\item exclude all participants' evaluations, who did {\bf not} share their {\bf demographic information} (age, gender education level -- all three pieces of information are either missing or all present).
\item exclude participants' records, if {\bf none of the evaluations}  correctly identified the data plot -- every participant was shown a range of `easy' lineups.
\item include participants' records, if   {\bf at least 20 percent} of the evaluations are {\bf correct}  -- based on ten evaluations per participants, two correct evaluations are significant evidence against a person just guessing
\item include participants' records, if at least {\bf 50\% of all very easy lineups are correct} 
\item use easy lineups as {\bf reference charts}: sample one easy lineup from a person's records. If that lineup is evaluated {\bf correctly}, include all (other) lineups of that person, otherwise exclude all lineup evaluations by this participant.
\end{enumerate}

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying six screening process on all three experimental data sets. 
\hh{Note that in some of the lines the number of male and female participants does not add up to the total number of participants. This is due to missing demographic information.}}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & Subj & Male & Fem & Total & Subj & Male & Fem & Total & Subj & Male & Fem & Total \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
  6 & 239 & 121 & 107 & 2317 & 351 & 185 & 164 & 3858 &  98 &  64 &  34 & 1095 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_log_counts.pdf}}
       \caption{Frequency of plot picks by log$_10$ $p$-value in all of the sixty (60) individual lineups for experiment 1. The colored lines indicate the $p$-value of observed data plot.}
       \label{fig:P-val_log}
\end{figure*}
